\LARGE \bf Cross Validation of Emotional Features with a non-Anthropomorphic Platform

### 2017-01-25 RO-MAN-2017-1/Parts/CaseStudy.tex
New version of the last case study

The case study was done at Researcher's Night 2015 with two main objectives:
\begin{enumerate}
	\item Cross-validate the findings obtained from a previous experiment~\cite{Angel2017-2}. This experiment was done to study the attribution of different linear and angular velocities, oscillation angel, direction and orientation of the platform to \textit{Anger}, \textit{Happiness}, \textit{Sadness} and \textit{Fear}. A total of 196 were designed, but just 20 treatments were presented to each participant. The questionnaire provided included the four emotions and two mental states (i.e. Excitement and tenderness).
	\item Verify if participants would prefer scenes when the robot expresses emotions or rather moves without any emotion expression. 
\end{enumerate}
To reduce scene variability was used two web-cams and eight Alvar tags to informed a Kalman filter to improve robots localization in the stage. AR tags were detected using the ROS package ar\_track\_alvar~\cite{artag2015}. The distribution of the web-cams and the tags are depicted in Figure~\ref{fig:setup_fourth}.

@@

@@

The parameters selected from the experiment to express \textit{Anger}, \textit{Happiness}, \textit{Sadness} and \textit{Fear} are shown in Table~\ref{table:selected_fourth}. As it could be observed, two implementations of each emotions were selected. These implementations were selected considering: (i) the linear velocity should be greater than $0$. In other words the robot should show some linear displacement. And (ii) it should be in the top 10 list of the emotion obtained in the experiment.

@@

This case study was done during Researchers' Night, 2015. During a period of two days, people were asked to participate to this study, which was divided in to parts. In the first one, each subject was exposed to two rounds of emotions. The emotion presented and the order were generated randomly before hand. In the second part, they were explained that a small scene was going to be presented twice. Thus, they should to selected the one they like it more. The order of the scenes (e.g. with or without emotion) were generated beforehand. The total number of volunteers was 256: 128 males, 126 females, and 2 that chose not to specify their gender. The average age was 27.29 years, with standard deviation of 16.58, minimum age was 4 and maximum 76.

>>>>

The case study presented in this paper was done at Researcher's Night 2015 with two main objectives:
\begin{enumerate}
	\item Cross-validate the findings obtained from a previous experiment~\cite{Angel2017-2}. This experiment was done to study the attribution of different linear and angular velocities, oscillation angel, direction and orientation of the platform to \textit{Anger}, \textit{Happiness}, \textit{Sadness} and \textit{Fear}. A total of 196 treatments were designed, but just 20 were presented to each participant. The questionnaire provided included the four emotions and two mental states (i.e. Excitement and tenderness).
	\item Verify if participants would prefer scenes when the robot expresses emotions or rather moves without any emotion expression. To reduce scene variability was used two web-cams and eight Alvar tags to informed a Kalman filter to improve robots localization in the stage. AR tags were detected using the ROS package ar\_track\_alvar~\cite{artag2015}. The distribution of the web-cams and the tags are depicted in Figure~\ref{fig:setup_fourth}.

@@

\end{enumerate}

@@

The parameters selected from the experiment to implement \textit{Anger}, \textit{Happiness}, \textit{Sadness} and \textit{Fear} are shown in Table~\ref{table:selected_fourth}. As it could be observed, two treatments for each emotions were selected to be implemented. These treatments were selected considering: (i) the linear velocity should be greater than $0$. In other words the robot should show some linear displacement. And (ii) it should be in the top 10 list of the emotion obtained in the experiment.

@@

This case study was done during Researchers' Night, 2015. During a period of two days, people were asked to participate in this study, which was divided in to parts. The first one, each subject was exposed to two rounds of emotions. The two emotions and their other were generated randomly before hand. The second part, participants were explained that a small scene was going to be presented twice. Thus, they should to selected the one they like more. The order of the scenes (e.g. with or without emotion) were generated beforehand. The total number of volunteers was 256: 128 males, 126 females, and 2 that chose not to specify their gender. The average age was 27.29 years, with standard deviation of 16.58, minimum age was 4 and maximum 76.

### 2017-01-25 RO-MAN-2017-1/Parts/Introduction.tex
New version of the last case study

Emotions and mental states are not just expressed through facial expression but also by body through postures and other features~\cite{Gelder2008}. Many psychological studies have been focused on understanding the role of human face in emotion projection~\cite{Ekman2004},~\cite{kleinsmith2012affective} and mental states. This trend has been followed by the robotics community, where anthropomorphic faces (e.g.,~\cite{Arras2012},~\cite{Breazeal2002}) and bodies (e.g.,~\cite{Canamero2010},
%~\cite{haering2011},
~\cite{Destephe2013}
) have been used to convey emotions.
However in many situations presence of anthropomorphic elements would be out of place and not justified by the main robot's functionalities. Most of the current and future robotics platforms on the market will not require anthropomorphic faces~\cite{Breazeal2002} or limbs~\cite{Li2011}, for instance in floor cleaning robots, anthropomorphic characteristics could even be detrimental to robot's task accomplishment.
This generates the necessity to study other mechanisms that could help to project emotions, which could give people an idea about the robots' state, and engage the user in long term relations.

It has been noticed that the amount of works studying non-anthropomorphic features in robotics (e.g.,~\cite{Saerbeck2010}
%,Lakatos2014,Sharma2013,Novika2015}
) remains still small in comparison to those exploiting anthropomorphic features. Moreover, these works do not give specific range of values for the characteristics used to expressed  emotions implemented. For example Suk and collaborators~\cite{NAM2014} in their study give specific values for acceleration and curvature,  but their connection to specific emotions is not explicited. Rather, they establish a relationship between their values and pleasure/arousal dimensions. This could help to select specific features to convey certain emotions, but it would be even better to know the precise range of values to be assigned to each characteristics to avoid  misinterpretation with wrong emotions. These values could be used in social robotics to show emotions and as consequence increase their acceptance.

>>>>

Emotions and mental states are not just expressed through facial expression and voice but also by body postures and other features~\cite{Gelder2008}. Many psychological studies have focused their attention on how emotions are conveyed through they face~\cite{Ekman2004},~\cite{kleinsmith2012affective}. Similarly, the robotics community uses anthropomorphic faces (e.g.,~\cite{Arras2012},~\cite{Breazeal2002}) and bodies (e.g.,~\cite{Canamero2010},
%~\cite{haering2011},
~\cite{Destephe2013}
) to convey emotions.
In many situations presence of anthropomorphic elements would be out of place and not justified by the main robot's functionalities. Most of the current and future robotics platforms on the market will not require anthropomorphic faces~\cite{Breazeal2002} or limbs~\cite{Li2011}. For instance, floor cleaning robots are robots that do not have any anthropomorphic characteristics and still they accomplish their task.
This generates the necessity to study other mechanisms that could help to convey emotions, which could give people an idea about the robots' state, and engage the user in long term relations.

However,the amount of works studying non-anthropomorphic features in robotics (e.g.,~\cite{Saerbeck2010}
%,Lakatos2014,Sharma2013,Novika2015}
) remains still small in comparison to those exploiting anthropomorphic features. Moreover, these works do not give specific range of values for the characteristics used to expressed the emotions implemented. For example Suk and collaborators~\cite{NAM2014} in their study give specific values for acceleration and curvature,  but their connection to specific emotions is not described. Rather, they established a relationship between their values and pleasure/arousal dimensions. This could help to select specific features to convey certain emotions, but it would be even better to know the precise range of values to be assigned to each characteristics to avoid  misinterpretation with wrong emotions. These values could be used in social robotics to show emotions and as consequence increase their acceptance.

### 2017-01-25 RO-MAN-2017-1/Parts/RelatedWork.tex
New version of the last case study

Most of the works done in Human-Robot Interaction (HRI) have focused on faces, due to the abundance of works in face elicitation in humans. One of the most well-known expressive robots is Kismet~\cite{Breazeal2002}, a robotic face able to interact with people and to show emotions. The face had enough degrees of freedom to portray the basic emotions suggested by Ekman~\cite{Ekman2004} (\textit{Happiness}, \textit{Surprise}, \textit{Anger}, \textit{Disgust}, \textit{Fear}, and \textit{Sadness}), plus interest. 
Despite the complex system behind Kismet, the emotion's projection evaluation was done using videos with a very limited number of participants. Similar approach was followed by Li and Chignell~\cite{Li2011}, who used videos of a teddy bear robot to study the contribution of arms and head movement to express emotions. In same direction Destephe and collaborators~\cite{Destephe2013} studied the attribution of emotion to a robot's gait using a virtual representation of the platform WABIAN-2R. Knight and Simmons~\cite{knight2016} used two platforms (i.e. Keepon and NAO) with different degrees of freedom to study the possibility to project inner states with just head movements. Although the use of videos has the advantage to cover a major number of participants, they loss the impact that is created from the interaction between the participant and the platform.

%%%%%%%%%%%%%%%%%%%%%%%%
The use of real platforms to study emotion projection could be dissect by the type of platform used. Therefore two tendencies could been observed: use of anthropomorphic and non-anthropomorphic platforms. In the first case, these works are characterized by the use of cue positions to project desire emotions~\cite{NAO2013}. In some cases, special attention has been taken to determine head's angle and arms position contribution in specific emotions~\cite{Brown2014}. 
Nevertheless, current humanoid platforms cannot generate smooth gaits, which limit the study of body movements. To overcome this limitation, some researchers have reduce the human appearance (e.g. eliminating limps and facial expressions)to increase platform mobility and study new mechanisms to project emotions~\cite{Arras2012}. Trying to reduce the anthropomorphism, Saerbeck and Christoph used a Roomba platform to study the contribution of curvature in a trajectory to conceive emotional states~\cite{Saerbeck2010}. Similarly Lourens and Barakova~\cite{BarakovaL10} implemented a set of behaviors to determine the emotion  perceived from diverse movements, which were selected from the  work done by Camurri et al.~\cite{pop00002}. Continuing with her research on how robotics' behaviours are interpreted by people, Barakova and collaborators~\cite{Barakova2013} created a closet in which lights could be manipulated to convey pre-defined behaviours. The robot's behaviours were defined using the Interpersonal Behaviour Circle (ICB)~\cite{Leary57}, which is based on two dimensions (dominance-submission and hate-love). Their findings suggest that electronic systems can elicit a type of reactions different from the one expected by theories of interpersonal communication.

Other approaches have tried to get a better understanding of the contribution of diverse features to express emotions through movement. For example, Suk and collaborators payed a particular attention to speed, smoothness, granularity of movement path and volume of a non-bioinspired object~\cite{NAM2014}. Their results suggest that arousal increases as speed increases and that there is not any clear tendency for smoothness. On the other hand, granularity is positively correlated with pleasure and arousal, while volume is negatively correlated with pleasure and positively correlated with arousal. Alike, Tan and collaborators~\cite{Tan2016} have studied the contribution of velocity, fluidity, direction and orientation of a small box. Their results suggest that direction is directly correlated with dominance, but that fluidity does not influence the perception. While flat orientation is related to positive valence, leaning position are related with negative valance. Finally the velocity is correlated with valence, arousal and dominance.

>>>>

%Most works in Human-Robot Interaction (HRI) focus their attention on faces and human-like bodies, due to the abundance of works in face elicitation in humans. Moreover, 
Some works in Human-Robot Interaction (HRI) uses videos to evaluate their implementations of emotions. One of the most well-known expressive robots is Kismet~\cite{Breazeal2002}, a robotic face able to interact with people and show emotions. The face had enough degrees of freedom to portray the emotions suggested by Ekman~\cite{Ekman2004} (\textit{Happiness}, \textit{Surprise}, \textit{Anger}, \textit{Disgust}, \textit{Fear}, and \textit{Sadness}), plus interest. 
Despite the complex system behind Kismet, the emotion's projection evaluation was done using videos with a very limited number of participants. Similar approach was followed by Li and Chignell~\cite{Li2011}, who used videos of a teddy bear robot to study the contribution of arms and head movement to express emotions. In same direction Destephe and collaborators~\cite{Destephe2013} studied the attribution of emotion to a robot's gait using a virtual representation of the platform WABIAN-2R. Knight and Simmons~\cite{knight2016} used two platforms (i.e. Keepon and NAO) with different degrees of freedom to study the possibility to project inner states with just head movements. Although the use of videos has the advantage to cover a major number of participants, they loss the impact that is created from the interaction between the participant and the platform.

%%%%%%%%%%%%%%%%%%%%%%%%
The use of real platforms to study emotion projection could be dissect in two tendencies: use of anthropomorphic and non-anthropomorphic platforms. In the first case, these works are characterized by the use of cue positions to project desire emotions~\cite{NAO2013}. In some cases, special attention has been taken to determine head's angle and arms position contribution in specific emotions~\cite{Brown2014}. 
Nevertheless, current humanoid platforms cannot generate smooth gaits, which limit the study of body movements. To overcome this limitation, some researchers have reduce the human resemblance (e.g. eliminating limps and facial expressions)to increase platform mobility and study new mechanisms to project emotions~\cite{Arras2012}. Reducing even more the anthropomorphism, Saerbeck and Christoph used a Roomba platform to study the contribution of curvature in a trajectory to conceive emotional states~\cite{Saerbeck2010}. Similarly Lourens and Barakova~\cite{BarakovaL10} implemented a set of behaviors to determine the emotion  perceived from diverse movements, which were selected from the  work done by Camurri et al.~\cite{pop00002}. Continuing with her research on how robotics' behaviours are interpreted by people, Barakova and collaborators~\cite{Barakova2013} created a closet in which lights could be manipulated to convey pre-defined behaviours. The robot's behaviours were defined using the Interpersonal Behaviour Circle (ICB)~\cite{Leary57}, which is based on two dimensions (dominance-submission and hate-love). Their findings suggest that electronic systems can elicit a type of reactions different from the one expected by theories of interpersonal communication. Despite the type of platform used, these works offers an overview of features that could be used to express certain emotions but they not give precise values to implement the emotions.

Therefore, other approaches have tried to get a better understanding of the contribution of diverse features to express emotions through movement. For example, Suk and collaborators payed a particular attention to speed, smoothness, granularity of movement path and volume of a non-bioinspired object~\cite{NAM2014}. Their results suggest that arousal increases as speed increases and that there is not any clear tendency for smoothness. On the other hand, granularity is positively correlated with pleasure and arousal, while volume is negatively correlated with pleasure and positively correlated with arousal. Alike, Tan and collaborators~\cite{Tan2016} have studied the contribution of velocity, fluidity, direction and orientation of a small box. Their results suggest that direction is directly correlated with dominance, but that fluidity does not influence the perception. While flat orientation is related to positive valence, leaning position are related with negative valance. Finally the velocity is correlated with valence, arousal and dominance.

### 2017-01-25 RO-MAN-2017-1/Parts/Results.tex
New version of the last case study

To have a clear idea about these misinterpretations among implemented emotions, a Fisher's exact test was applied for ten different combinations. Additionally, a Holm-Bonferroni correction was applied for multiple comparisons to get a better p-value estimation. The results are reported in Table~\ref{table:result_compare_fourth}. The following are the hypothesis used for this test:

\begin{itemize}
	\item $H_0 = $ there is a difference in the recognition of the two compared implementations.
	\item $H_1 = $ there is not a difference in the recognition of the two compared implementations.
\end{itemize}

As this analysis suggest, both implementation of \textit{Anger} were perceived as two different emotions. Also shows that both implementation of \textit{Happiness} were perceived as similar to Anger-2.

\begin{table}
\centering
\small
\caption{Pair comparison among all the implemented emotions using Fisher's exact test for both questionnaires with $\alpha = 0.05$ for the  case study. The * indicates that the p-value was adjusted using the Holm-Bonferroni correction for multiple comparisons.}
		\label{table:result_compare_fourth}
		\begin{tabular}{|c|c|c|}
			\hline	
\textbf{Pair Compared} & \textbf{p-value} & \textbf{p-value*}\\	
			\hline
			Happiness-1 vs Happiness-2 &$0.38$&$1.0$\\
			\hline
			Anger-1 vs Anger-2 & $<0.001$ 
			%7.3e-4
			& $<0.001$
			%4.4e-3
			\\
			\hline
			Anger-2 vs Happiness-1 & $0.137$&$0.69$\\
			\hline
			Anger-2 vs Happiness-2 & $0.157$&$0.69$\\
			\hline
			Fear-1 vs Fear-2 & $0.74$&$1.0$\\
			\hline
			Sadness-1 vs Sadness-2 & $0.665$&$1.0$\\
			\hline
			Fear-1 vs Sadness-1& $<0.001$ 
			%8.35e-5
			& $<0.001$
			%5.8e-4
			\\
			\hline
			Fear-1 vs Sadness-2 & $<0.001$
			%5e-7
			& $<0.001$
			%4e-6
			\\
			\hline
			Fear-2 vs Sadness-1 & $<0.001$
			%2e-7
			& $<0.001$
			%1.8e-6
			\\
			\hline
			Fear-2 vs Sadness-2 & $<0.001$
			%1e-7
			& $<0.001$
			%1e-6
			\\
			\hline
			\end{tabular}
\end{table} 
Moreover, an analysis was done per groups, for each presented emotion. For each emotion it was considered how many subjects in each group recognized it, how many identified a different emotion, how many identified the considered emotion when presented another one, and how many subjects recognized an emotion different from the considered one when presented a different emotion. This lead to a table, for each presented emotion, like the one reported in table~\ref{table:singleEmotion} for Happiness-1. 
\begin{table}[!htbp]
\begin{center}
\caption{Example of table compiled for each emotion on the subjects which have been presented each emotion (here Happiness-1).}
\label{table:singleEmotion}
\begin{tabular}{|c|c|c|}
\hline 
Presented/Reported&Happiness&Other\\
\hline 
Happiness-1&8&54\\
\hline 
Other&42&355\\
\hline
\end{tabular}
\end{center}
%\vspace{-0.5cm}
\end{table}

For each table the positive predictive value, accuracy and a Pearson's $\chi^2$ were computed. The results are shown in table~\ref{table:Precision2}. The following are the hypothesis used for this test:

@@

They show that there is significant evidence to conclude that Anger-2, both of \textit{Fear} and \textit{Sadness} are considered as a different implementation when they are compare with the others. While both implementation of \textit{Happiness} and Anger-1 are considered as similar to the other implementations. %TODO make clear this part

@@

 For each of the contingency table the classification accuracy and the no-information rate (NIR), i.e. the accuracy that had been obtained by random selection, are reported in Table~\ref{table:nir_fourth}. The results reveal that Sadness-2 is the only implementation that was correctly recognized among all implementations ($p<0.05$). 
Nevertheless, it is important no notice that the results were obtained using the lower part of the robot without any change in shape. Another important factor to highlight is the impact words listed in the questionnaire have on the perception rate. As it was expected, mental states Excitement and Tenderness were confused with emotions with similar arousal level. In this precise case the emotions Anger, Happiness and Fear were confused with Excitement, and Sadness was confused with Tenderness. Despite the bias generated by the two mental states listed in the questionnaire, the recognition rate of five out of eight implementations was over 35\%, being the two implementation of \textit{Fear} the implementations with the higher recognition rates (54\% for the first and 50\% for the second).

>>>>

An analysis was done per groups, for each presented emotion. For each emotion it was considered how many subjects in each group recognized it, how many identified a different emotion, how many identified the considered emotion when presented another one, and how many subjects recognized an emotion different from the considered one when presented a different emotion. This lead to a table, which is known as contingency table, for each presented emotion, like the one reported in table~\ref{table:singleEmotion} for Happiness-1. 
\begin{table}[!htbp]
\begin{center}
\caption{Example of table compiled for each emotion on the subjects which have been presented each emotion (here Happiness-1).}
\label{table:singleEmotion}
\begin{tabular}{|c|c|c|}
\hline 
Presented/Reported&Happiness&Other\\
\hline 
Happiness-1&8&54\\
\hline 
Other&42&355\\
\hline
\end{tabular}
\end{center}
%\vspace{-0.5cm}
\end{table}

For each of the contingency table the classification accuracy and the no-information rate (NIR), i.e. the accuracy that had been obtained by random selection, are reported in Table~\ref{table:nir_fourth}. The results reveal that Sadness-2 is the only implementation that was correctly recognized among all implementations ($p<0.05$).

Additionally, the positive predictive value, accuracy and a Pearson's $\chi^2$ were computed for each table. The hypothesis used in the test were:

@@

The results are shown in table~\ref{table:Precision2}. They show that there is significant evidence to conclude that Anger-2, both of \textit{Fear} and \textit{Sadness} are considered as a different implementation when they are compare with other implementations. While both implementations of \textit{Happiness} and Anger-1 are considered as similar to the other implementations.

@@

To determine if which implementations were perceived as different or similar, a Fisher's exact test was applied for ten different combinations of the implementations. Additionally, a Holm-Bonferroni correction was applied for multiple comparisons to get a better p-value estimation. The following are the hypothesis used in this test:

\begin{itemize}
	\item $H_0 = $ there is a difference in the recognition of the two compared emotions.
	\item $H_1 = $ there is not a difference in the recognition of the two compared emotions.
\end{itemize}

The results are reported in Table~\ref{table:result_compare_fourth}. As it could be observed, both implementation of \textit{Anger} were perceived as two different emotions ($p<0.001$). Also shows that both implementation of \textit{Happiness} were perceived as to Anger-2 ($p=0.69$ in both cases).

\begin{table}
\centering
\small
\caption{Pair comparison among all the implemented emotions using Fisher's exact test for both questionnaires with $\alpha = 0.05$ for the  case study. The * indicates that the p-value was adjusted using the Holm-Bonferroni correction for multiple comparisons.}
		\label{table:result_compare_fourth}
		\begin{tabular}{|c|c|c|}
			\hline	
\textbf{Pair Compared} & \textbf{p-value} & \textbf{p-value*}\\	
			\hline
			Happiness-1 vs Happiness-2 &$0.38$&$1.0$\\
			\hline
			Anger-1 vs Anger-2 & $<0.001$ 
			%7.3e-4
			& $<0.001$
			%4.4e-3
			\\
			\hline
			Anger-2 vs Happiness-1 & $0.137$&$0.69$\\
			\hline
			Anger-2 vs Happiness-2 & $0.157$&$0.69$\\
			\hline
			Fear-1 vs Fear-2 & $0.74$&$1.0$\\
			\hline
			Sadness-1 vs Sadness-2 & $0.665$&$1.0$\\
			\hline
			Fear-1 vs Sadness-1& $<0.001$ 
			%8.35e-5
			& $<0.001$
			%5.8e-4
			\\
			\hline
			Fear-1 vs Sadness-2 & $<0.001$
			%5e-7
			& $<0.001$
			%4e-6
			\\
			\hline
			Fear-2 vs Sadness-1 & $<0.001$
			%2e-7
			& $<0.001$
			%1.8e-6
			\\
			\hline
			Fear-2 vs Sadness-2 & $<0.001$
			%1e-7
			& $<0.001$
			%1e-6
			\\
			\hline
			\end{tabular}
\end{table}

Nevertheless, it is important no notice that the results were obtained using the lower part of the robot without any change in shape. Another important factor to highlight is the impact words listed in the questionnaire have on the perception rate. As it was expected, mental states Excitement and Tenderness were confused with emotions with similar arousal level. In this precise case the emotions Anger, Happiness and Fear were confused with Excitement, and Sadness was confused with Tenderness. Despite the bias generated by the two mental states listed in the questionnaire, the recognition rate of five out of eight implementations was over 35\%, being the two implementation of \textit{Fear} the implementations with the higher recognition rates (54\% for the first and 50\% for the second).

### 2017-01-25 RO-MAN-2017-1/Parts/System.tex
New version of the last case study

A non-anthropomorphic robotic platform was created to do not have any bio-inspired appearance. The holonomic platform was built using Odroid U3, Arduino Due, and 3 metal gear motors with 64 CPR encoders and omniwheels. The platform could be observed in Figure~\ref{fig:Robot}. The Arduino Due is in charge to be the interface between the hardware (e.g. motors) and Odroid, which host all the Emotion Enrichment System.

\begin{figure}[t]
\centering%
\subfigure {\includegraphics[height=3cm]{./Images/DSC_0447.JPG}}
\hspace{2mm}
\subfigure{\includegraphics[height=3cm]{./Images/TriskarThird.png}}
\caption{Platform used in the case study (left), and holonomics's blue prints (right). The arrows represent robot's frame of reference.
\label{fig:Robot}}
\end{figure}
An Emotional Enrichment System was designed and implemented to automatize the process of emotion expression~\cite{Angel2017}. It modifies actions' parameters and adds additional actions to create the illusion of emotion expression in a robot. To achieve this, the system receives two messages. One message describes actions and the order in which they should be executed. These actions could be executed in parallel, sequentially or a combination of both. This kind of description enables the possibility to communicate several actions in one message. The other message informs the system with the desire emotion and its intensity. These two messages could arrive asynchronously and without any particular order. Every time a message is received, the system updates the robot movements to convey the desire emotion in the specific action.

>>>>

A non-anthropomorphic robotic platform was created to no influence participants' perception. The robotic platform is holonomic and it was built using Odroid U3, Arduino Due, and 3 metal gear motors with 64 CPR encoders and omniwheels. The platform could be observed in Figure~\ref{fig:Robot}. The Arduino Due is in charge to be the interface between the hardware (e.g. motors) and Odroid, which host all the Emotion Enrichment System.

\begin{figure}[t]
\centering%
\subfigure {\includegraphics[height=3cm]{./Images/DSC_0447.JPG}}
\hspace{2mm}
\subfigure{\includegraphics[height=3cm]{./Images/TriskarThird.png}}
\caption{Platform used in the case study (left), and holonomics's blue prints (right). The arrows represent robot's frame of reference.
\label{fig:Robot}}
\end{figure}

An Emotional Enrichment System was designed and implemented to automatize the process of emotion expression~\cite{Angel2017}. It modifies actions' parameters and adds additional actions to create the illusion of emotion expression in a robot. To achieve this, the system receives two messages. One message describes actions and the order in which they should be executed. These actions could be executed in parallel, sequentially or a combination of both. This kind of description enables the possibility to communicate several actions in one message. The other message informs the system with the desire emotion and its intensity. These two messages could arrive asynchronously and without any particular order. Every time a message is received, the system updates the robot movements to convey the desire emotion in the specific action.

### 2017-01-25 RO-MAN-2017-1/RO-MAN2017.tex
New version of the last case study

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Robots should be able to express emotional states to interact with people as social agents. Emotions are a peculiar characterization of humans and usually conveyed through face expression or body language. However there are cases where robots cannot have anthropomorphic shape, for example when they have to perform tasks, which require a specific structure. This is the case of home cleaners, package carriers, and many others platforms. Therefore, emotional states need to be represented by exploiting other features, such as movements and shape changes. The work presented in this paper studies emotion expression in non-anthropomorphic platform and how it is perceived by humans. The work uses results obtained from a previous experiment, which was done to assess precise values for linear velocity, angular velocity, oscillation angle, direction and orientation that could be used to express happiness, angry, fear and sadness. Results show that people can recognize some emotional expressions better than others and that additional features should be added to differentiate some emotions. Additionally, it was done a small scene to verify if people prefer emotions with or without emotion. 
\end{abstract}

\section{Introduction}
\input{./Parts/Introduction}
\label{sec:related_work}
\section{Related Work}
\input{./Parts/RelatedWork}
\section{System}
\label{sec:system}
\input{./Parts/System}
\section{Case Study}
\label{sec:case}
\input{./Parts/CaseStudy}
\section{Results}
\label{sec:results}
\input{./Parts/Results}
\section{Conclusions and Further work}
\input{./Parts/Conclusions}
\bibliographystyle{IEEEtran}
\bibliography{Bibliography,BibloNew,Biblography}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Robots should be able to express emotional states to interact with people as social agents. Emotions are a peculiar characterization of humans and usually conveyed through face expression, body language and voice. However there are cases where robots cannot have anthropomorphic shape, for example when they have to perform tasks, which require a specific structure. This is the case of home cleaners, package carriers, and many others platforms. Therefore, emotional states need to be represented by exploiting other features, such as movements and shape changes. This paper presents a case study, which studies emotion expression in non-anthropomorphic platform and how it is perceived by humans. This case study was design base on results obtained from a previous experiment, which was done to assess precise values for linear velocity, angular velocity, oscillation angle, direction and orientation that could be used to express happiness, angry, fear and sadness. Results of the case study  show that people can recognize some emotional expressions better than others and that additional features should be added to differentiate some emotions. Additionally, it was done a small scene to verify if people prefer emotions with or without emotion. 
\end{abstract}

\section{Introduction}
\input{./Parts/Introduction}
\section{Related Work}
\label{sec:related_work}
\input{./Parts/RelatedWork}
\section{System}
\label{sec:system}
\input{./Parts/System}
\section{Case Study}
\label{sec:case}
\input{./Parts/CaseStudy}
\section{Results}
\label{sec:results}
\input{./Parts/Results}
\section{Conclusions and Further work}
\input{./Parts/Conclusions}
\bibliographystyle{IEEEtran}
\bibliography{Bibliography,BibloNew,Biblography}
